\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}

### 2016-03-29 tex/paper.tex
Added Findings and Prior work

%}}}
\title{\textbf{Perius: A Security Management Layer with Copy-on-Write for CDN Assets}}
\author{Klingsbo, Lukas}

@@

@@

\begin{lstlisting}[label=JPFRESULT,caption=Results of JPF run]
elapsed time:       14:26:53
states:             new=160853259,
                    visited=451102505,
                    backtracked=611955764,
                    end=21640
search:             maxDepth=380,
                    constraints=0
choice generators:  thread=160853255 
                    (signal=0,
                    lock=3603938,
                    sharedRef=146989208,
                    threadApi=3,
                    reschedule=10260106), 
                    data=0

@@

instructions:       11917045758
max memory:         6256MB
loaded code:        classes=111,
                    methods=2179
\end{lstlisting}

@@

\subsubsection{Security}
The greatest security improvement of Perius compared to its predecessor Battlebinary is not the
security of the system itself but rather how Perius handles the contents security settings on the
CDN providers. Perius uses several of the security features for private content that the CDN
providers offer (see Section~\ref{sec:private_content}) to make sure that the content only is
accessible from where it should be. In Battlebinary the content was secured by adding a part of the
hash of the file (see Section~\ref{sec:current_system}) to the filename that it was uploaded with, 
which resulted in a URL on the CDN that was not guessable but if the link somehow leaked the 
content that the link referred to would be open to anyone.

\subsubsection{Scalability}
When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enormous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak, as discussed in 
Section~\ref{sec:GET_REQUESTS}, for what Casbah can handle on a single server.

@@

\par These are very simple requests, to evaluate how much load the application can handle in its
current state, a more complex but common request has to be analysed. The most complicated and still
common request that the system is receiving is requests of a full project tree. This request is
computationally expensive as the tree is not stored directly in the database but has to be built
from the ID and parent ID of each container and content. A simulated project tree of similar size to
the ones stored in the current management system reaches around 25KB in uncompressed size.

@@

\newpage
\section{Discussion}
This chapter contains informal discussions about topics that were not covered by the rest of the
report but that are still significant enough to mention.

>>>>

%}}}
\title{\textbf{Providing Access Control and Copy-on-Write for Content Distribution Network Assets}}
\author{Klingsbo, Lukas}

@@

\subsubsection{Snapshots}
Several filesystems~\cite{BTRFS}\cite{ZFS} use snapshot techniques to make it possible for a user
or system to roll back the filesystems state, to a state that the filesystem had at the time of
snapshot creation. This can be useful for example when having a stable system and then doing a
system update, if the system does not respond well to the update the filesystem can be rolled
back to its previous stable state, provided that a snapshot was created before the update procedure.

@@

\begin{minipage}{\linewidth}
\begin{lstlisting}[label=JPFRESULT,caption=Results of JPF run]%,float,floatplacement=H]
elapsed time:       14:26:53
states:             new=160853259,
                    visited=451102505,
                    backtracked=611955764,
                    end=21640
search:             maxDepth=380,
                    constraints=0
choice generators:  thread=160853255 
                    (signal=0,
                    lock=3603938,
                    sharedRef=146989208,
                    threadApi=3,
                    reschedule=10260106), 
                    data=0

@@

instructions:       11917045758
max memory:         6256MB
loaded code:        classes=111,
                    methods=2179
\end{lstlisting}
\end{minipage}

@@

\subsubsection{Security}
The greatest security improvement of Perius compared to its predecessor Battlebinary is not the
security of the system itself but rather how Perius handles the contents security settings on the
CDN providers. Perius uses several of the security features for private content that the CDN
providers offer (see Section~\ref{sec:private_content}) to make sure that the content only is
accessible from where it should be. In Perius it is possible to have three different modes for a CDN
asset; public to all, only accessible from certain IP ranges or only accessible by clients using a
signed URL or cookie. In Battlebinary the content was secured by adding a part of the hash of the
file (see Section~\ref{sec:current_system}) to the filename that it was uploaded with, which
resulted in a URL on the CDN that was not guessable but if the link somehow leaked the content that
the link referred to would be open to anyone.

\newgeometry{top=4cm}
\subsubsection{Scalability}
Perius uses MongoDB as its persistent storage and all computationally expensive operations involve
doing calls to it. Scala currently has two popular drivers for interaction with MongoDB, namely
Casbah and ReactiveMongo.

When using the ReactiveMongo driver~\cite{REACTIVEMONGO}, which is asynchronous and non-blocking, 
the application has no limits of how much load and users it can handle as the hardware and nodes 
can be scaled up linearly when needed. With Cashbah~\cite{CASBAH}, which is used with the current 
implementation, it is harder to scale to the enormous amounts of load which ReactiveMongo can 
support as Casbah is synchronous and has blocking IO. For this work the kind of scalability which 
is offered by ReactiveMongo is not needed as the load will not reach the peak, as discussed in 
Section~\ref{sec:GET_REQUESTS}, for what Casbah can handle on a single server.

@@

\par These are very simple requests, to evaluate how much load the application can handle in its
current state, a more complex but common request was analysed. The most complicated and still
common request that the system is receiving is requests of a full project tree. This request is
computationally expensive as the tree is not stored directly in the database but has to be built
from the ID and parent ID of each container and content. A simulated project tree of similar size to
the ones stored in the current management system reaches around 25KB in uncompressed size.

@@

\restoregeometry
\newpage
\section{Discussion}
This chapter contains informal discussions about topics that were not covered by the rest of the
report but that are still significant enough to mention.
